
% 中英文摘要和关键字
% 中文摘要
\renewcommand{\abstractname}{摘要} % 将 abstract 标题改为“摘要”
\begin{abstract}
微波原理课程是电子信息工程、通信工程及相关专业的重要基础课程，主要研究微波技术的基本理论和应用。本课程系统地介绍了微波的基本概念、特性及其在现代通信、雷达、遥感等领域的广泛应用。以下是该篇论文的具体结构划分。

第 1 章绪论介绍微波的基本概念和特性以及微波技术的发展和应用领域；第 2 章从“路”的观点出发，讲述传输线的基本理论，介绍反射系数、驻波比、输入阻抗、阻抗圆图和阻抗匹配等概念；第 3 章从“场”的观点出发，讲述波导、同轴线、带状线和微带线等典型微波传输线的一般理论和特性，给出常用的电磁波型、场分布和相应参数等；第 4 章采用“场”与“路”相结合的方法，讲述微波网络的基本理论，其中包括微波网络参量、网络矩阵和工作特性参量；第 5 章介绍各种常用微波元件的工作原理和应用。


\end{abstract}

% 中文关键词
\noindent \textbf{关键词：} 
微波原理，
传输线理论，
阻抗匹配，
微波网络，
微波元件，
波导，
同轴线，
带状线，
微带线，
电磁场分布，
网络矩阵，
工作特性参量
\addcontentsline{toc}{section}{摘要} % 将摘要添加到目录中

\; 

\renewcommand{\abstractname}{Abstract} % 恢复为默认的“Abstract”


\begin{abstract}
Microwave Principles is an essential foundational course for students in electronic information engineering, communication engineering, and related fields. It primarily focuses on the basic theories and applications of microwave technology. This course systematically introduces the fundamental concepts, characteristics, and widespread applications of microwaves in modern communications, radar, remote sensing, and other fields. The following is the specific structure of this paper.

Chapter 1 provides an introduction to the basic concepts and characteristics of microwaves, as well as the development and application areas of microwave technology. Chapter 2 discusses the basic theory of transmission lines from the perspective of "lines," introducing key concepts such as reflection coefficient, standing wave ratio, input impedance, Smith chart, and impedance matching. Chapter 3 explains the general theory and characteristics of typical microwave transmission lines, including waveguides, coaxial cables, strip lines, and microstrip lines, from the perspective of "fields." It also presents commonly used electromagnetic wave types, field distributions, and relevant parameters. Chapter 4 combines the perspectives of "fields" and "lines" to introduce the basic theory of microwave networks, covering microwave network parameters, network matrices, and operational characteristic parameters. Chapter 5 describes the working principles and applications of various common microwave components.


\end{abstract}

% 英文关键词
\noindent \textbf{Keywords:}
Microwave principle,
Transmission line theory,
Impedance matching,
Microwave network,
Microwave components,
Waveguide,
Coaxial line,
Strip line,
Microstrip line,
Electromagnetic field distribution,
Network matrix,
Operating characteristic parameters

\addcontentsline{toc}{section}{Abstract} % 将摘要添加到目录中
